Lyman-$\alpha$ photons through rotating outflows

### 2018-03-28 paper/paper.tex
muse in appendix temporarly and cite to theorem

where each $m_i$ is the i-th moment about the mean. The STD has velocity units and 
quantifies the dispersion of the line's velocity: the larger it is, the wider the line. 
The SKW is adimensional and quantifies the peaks' asymmetry: if it is $>0$ the left peak is 
taller and if it is $<0$ the right peak is taller. The BI is adimensional and
quantifies if the line has 1 or 2 peaks: it is  always $\geq 1$ and the closer it is to 1, the 
more bimodal is the line (i.e. has 2 peaks).

@@

>>>>

where each $m_i$ is the i-th moment about the mean. The STD has velocity units and 
quantifies the dispersion of the line's velocity: the larger it is, the wider the line. 
The SKW is adimensional and quantifies the peaks' asymmetry: if it is $>0$ the left peak is 
taller and if it is $<0$ the right peak is taller. The BI is adimensional and
quantifies if the line has 1 or 2 peaks: it is  always $\geq 1$ \citep{Pearson1929} and the closer it is to 1, the more bimodal is the line (i.e. has 2 peaks).

@@

% MUSE
\begin{figure*}
	\begin{center}
		\includegraphics[height=0.3\textheight]{./figures/appendix/muse_vs_simulations.pdf}
		\includegraphics[height=0.3\textheight]{./figures/appendix/museall_vs_muserange.pdf}
		\includegraphics[height=0.3\textheight]{./figures/appendix/muserange_vs_simulations.pdf}
	\end{center}
	\caption{\textbf{Caption:} Caption.
		\label{fig:varying_outflow}}
\end{figure*}
